Appendix S2: Data Exploration

### 2022-04-27 ms/data_exploration.Rmd
Fix URL for data in SI2

# Alternatively, unzip `results.zip`
# (FIXME: add DOI when available)
# and read in the data from there
# biodiv_ferns_cent_figshare <- read_csv(here::here("japan_ferns_biodiv.csv"))
```

>>>>

# Alternatively, download `results.zip` from
# https://figshare.com/ndownloader/files/34354472
# unzip it, and read in the data from there
# biodiv_ferns_cent_figshare <- read_csv(here::here("japan_ferns_biodiv.csv"))
```
